### 2022-05-27 Publish Paper/manuscript_main.tex
Update publish paper
- VN paper: abstract
- Eng paper: change std to mean, rewrite all

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{ACKNOWLEDGMENT} \\ 
I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung (dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project. He gave a chance to use High GPU computing computer for AI Training. Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.  
\section{Introduction}
%The Need of AI-enabled computer-aided diagnostics
Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99\%. However, once the disease progresses beyond the skin, survival is poor\cite{11872}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution. \newline
%The Need of AI-enabled computer-aided diagnostics in Skin Lesion Clasification
Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment. Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data. In Medical Treatment, AI models are applied to building solutions for a specific disease, medicine revolution is an example. In various studies, AI algorithms have provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}. \\
%The Success in AI - especially in CNN - some model based CNN
In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models wich have been used as a backbone model in this paper will be discuss more in the Related Work section. \\
In this paper, the effect of metadata on classifying skin disease is also analyzed .On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.

@@

%Other preprocessed input%

@@

%My proprocessed input%

@@

%Figure%

@@

However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class. The others still face the
the imbalanced term. Since this dataset is not balanced, therefore using augmented data can make the model bias to the class which has large sample. Using the metadata instead make the model less bias, though it still make the model imbalanced due to the high variance of model which has the number of depth much less than 400.\\ 

@@

		Model & akiec & bcc & bkl & df & mel & nv & vasc & $\sigma$ \\

@@

		DenseNet201 + Augmented Data & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.128 \\ 

@@

		InceptionResNetV2 + Augmented Data & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.225\\

@@

		Resnet50 + Augmented Data & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.165\\

@@

		VGG16 + Augmented Data & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.197\\ 

@@

		DenseNet201 + Metadata & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.088}\\

@@

		InceptionResNetV2 + Metadata & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.09}\\

@@

		Resnet50 + Metadata & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.162\\

@@

		Resnet152 + Metadata & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.199\\

@@

		MobileNetV2 + Metadata & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & 0.9 & 0.122\\

@@

		MobileNetV3Large + Metadata & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & 0.92 & 0.12\\

@@

		MobileNetV3Small + Metadata & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & 0.89 & 0.144\\

@@

		NasNetLarge + Metadata & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.088}\\

@@

		NasNetMobile + Metadata & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & 0.93 & 0.101\\

@@

	\caption{F1-Score of each class and the standard deviation of each model}

@@

		DenseNet201 + Augmented Data & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & \textbf{0.189}\\ 

@@

		InceptionResNetV2 + Augmented Data & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & \textbf{0.275}\\

@@

		Resnet50 + Augmented Data & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & \textbf{0.209}\\

@@

		VGG16 + Augmented Data & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 	\textbf{0.191}\\ 

@@

		DenseNet201 + Metadata & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & 0.116\\

@@

		InceptionResNetV2 + Metadata & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 	0.93 & \textbf{0.097}\\

@@

		Resnet50 + Metadata & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.107\\

@@

		Resnet152 + Metadata & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.121\\

@@

		MobileNetV2 + Metadata & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.126\\

@@

		MobileNetV3Large + Metadata & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & 0.12\\

@@

		MobileNetV3Small + Metadata & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.147\\

@@

		NasNetLarge + Metadata & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & 0.119\\

@@

		NasNetMobile + Metadata & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & 0.134\\

@@

	\caption{Recall score of each class and the standard deviation of each model}

@@

		MobileNetV3Large-Layer[:230] + Soft-Attention & s0.85 \\ 

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{ACKNOWLEDGMENT} \\ 
I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung (dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project. He gave a chance to use High GPU computing computer for AI Training. Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.  
\section{Introduction}
Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99 percent. However, once the disease progresses beyond the skin, survival is poor\cite{11872}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution. \\
Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment. Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data. In Medical Treatment, AI models are applied to building solutions for a specific disease, medicine revolution is an example. In various studies, AI algorithms have provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}. \\
In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models wich have been used as a backbone model in this paper will be discuss more in the Related Work section. \\
In this paper, the effect of metadata on classifying skin disease is also analyzed .On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.

@@

@@

@@

@@

However, only DenseNet201, InceptionResNetV2, and NasNetLarge whose depth are equal or larger than 400 have balanced f1-score on class. The others still face the imbalanced term. Since this dataset is not balanced, therefore using augmented data can make the model bias to the class which has large sample. Using the metadata instead make the model less bias, though it still make the model imbalanced due to the high variance of model which has the number of depth much less than 400.\\ 

@@

		Model & akiec & bcc & bkl & df & mel & nv & vasc & Mean \\

@@

		DenseNet201 + Augmented Data & 0.67 & 0.78 & 0.64 & 0.67 & 0.61 & 0.96 & 0.91 & 0.74 \\ 

@@

		InceptionResNetV2 + Augmented Data & 0.69 &	0.88 & 0.77 & 0.29 & 0.66 & 0.98 & 1 & 0.75\\

@@

		Resnet50 + Augmented Data & 0.53 & 0.86 & 0.68 & 0.67 & 0.57 & 0.97 & 0.95 & 0.74\\

@@

		VGG16 + Augmented Data & 0.65 & 0.7 & 0.52 & 0.4 & 0.53 & 0.95 & 0.95 & 0.67\\ 

@@

		DenseNet201 + WeightLoss & \textbf{0.84} & 0.77 & \textbf{0.81} & \textbf{0.83} & \textbf{0.69} & 0.94 & 0.97 & \textbf{0.83}\\

@@

		InceptionResNetV2 + WeightLoss & 0.77 & 0.83 & \textbf{0.83} & 0.64 & \textbf{0.75} & 0.94 & 0.7 & \textbf{0.81}\\

@@

		Resnet50 + WeightLoss & 0.49 & 0.59 & 0.55 & 0.36 & 0.45 & 0.83 & 0.8 & 0.58\\

@@

		Resnet152 + WeightLoss & 0.42 & 0.38 & 0.41 & 0.15 & 0.4 & 0.75 & 0.75 & 0.46\\

@@

		MobileNetV2 + WeightLoss & 0.68 & 0.79 & 0.66 & 0.78 & 0.54 & 0.9 & \textbf{0.9} & 0.75\\

@@

		MobileNetV3Large + WeightLoss & 0.72 & 0.76 & 0.75 & 0.92 & 0.58 & 0.92 & \textbf{0.92} & 0.79\\

@@

		MobileNetV3Small + WeightLoss & 0.6 & 0.72 & 0.61 & 0.75 & 0.47 & 0.89 & \textbf{0.89} & 0.70\\

@@

		NasNetLarge + WeightLoss & 0.79 & 0.79 & 0.8 & 0.74 & 0.65 & 0.92 & 0.92 & \textbf{0.80}\\

@@

		NasNetMobile + WeightLoss & 0.76 & 0.74 & 0.78 & 0.73 & 0.63 & 0.93 & \textbf{0.93} & 0.78\\

@@

	\caption{F1-Score of each class and the mean f1-score of each model}

@@

		DenseNet201 + Augmented Data & 0.52 & 0.77 & 0.58 & 0.5 & 0.71 & 0.97 & 1 & 0.72\\ 

@@

		InceptionResNetV2 + Augmented Data & 0.52 & 0.88 & 0.83 & 0.17 & 0.65 & 0.98 & 1 & 0.71\\

@@

		Resnet50 + Augmented Data & 0.43 & 0.85 & 0.7 & 0.5 & 0.47 & 0.98 & 0.9 & 0.69\\

@@

		VGG16 + Augmented Data & 0.61 & 0.81 & 0.44 & 0.44 & 0.68 & 0.95 & 0.9 & 0.69\\ 

@@

		DenseNet201 + Weight Loss & \textbf{0.85} & 0.75 & 0.78 & 0.83 & 0.63 & 0.96 & \textbf{1} & \textbf{0.82}\\

@@

		InceptionResNetV2 + Metadata & \textbf{0.82} & 0.84 & 0.81 & 0.67 & 0.7 & 0.95 & 	0.93 & \textbf{0.81}\\

@@

		Resnet50 + Weight Loss & 0.67 & 0.63 & 0.54 & 0.83 & 0.63 & 0.74 & 0.86 & 0.70\\

@@

		Resnet152 + Weight Loss & 0.51 & 0.49 & 0.35 & 0.76 & 0.47 & 0.63 & 0.48 & 0.52\\

@@

		MobileNetV2 + Weight Loss & 0.7 & 0.86 & 0.72 & 0.75 & 0.58 & 0.86 & \textbf{1} & 0.78\\

@@

		MobileNetV3Large + Weight Loss & 0.72 & 0.76 & 0.75 & \textbf{0.92} & 0.58 & 0.92 & 0.92 & \textbf{0.80}\\

@@

		MobileNetV3Small + Weight Loss & 0.76 & 0.84 & 0.68 & \textbf{1} & 0.52 & 0.82 & 0.93 & 0.79\\

@@

		NasNetLarge + Weight Loss & 0.73 & 0.71 & \textbf{0.83} & \textbf{0.92} & 0.59 & 0.9 & 0.93 & \textbf{0.81}\\

@@

		NasNetMobile + Weight Loss & \textbf{0.82} & 0.73 & \textbf{0.83} & \textbf{0.92} & 0.53 & 0.93 & 0.93 & \textbf{0.81}\\

@@

	\caption{Recall score of each class and the mean recall score of each model}

@@

		MobileNetV3Large-Layer[:230] + Soft-Attention & 0.85 \\ 
